Reviewer comments from PeerJ

### 2015-02-25 PeerJResponse.tex
Edits for PeerJ resubmission
Edits to introduction and response

\lev{So I have checked this. Their experimental design was with maize (don't know if that matters) but in low density plants were placed 36'' apart within rows and rows were 30'' apart. In the high density design plants were 12'' apart within rows and 30'' apart between rows. On each side of the row for the high density Helianthus annus was palnted 12'' away from seedlings to provide extra canopy cover.}

@@

\lev{I don't think this is necessary. Again, everyone has seemed to want something different in the intro. Last person wanted more maize/shade avoidance/tb1. Perhaps we can add a couple of sentences in about mex vs parv or the population stuff. I would like to not have to rewrite the entire intro again.}

\mbh{I might mention something briefly about \emph{parviglumis} being a ruderal species that can occur at high density (cite my \emph{Molecular Ecology} manuscript), but, no, I would not add a whole paragraph on the ecologies of the teosintes.}
\jri{this sounds OK. a wee bit of self-citation there hufford?}

>>>>

@@

\res{We have added a few sentences discussing population density of distribution of both \emph{Zea mays} ssp. \emph{parviglumis} and \emph{Zea mays} ssp. \emph{mexicana} to the introduction. This addition is reflected in the text on page 2, lines 22-26: ``Additionally, large, naturally-occurring populations of both \emph{parviglumis} and \emph{Zea mays} ssp. \emph{mexicana} (hereafter, \emph{mexicana}) can be found throughout Mexico \citep{Wilkes1977, Hufford2013}. \emph{parviglumis}, with \emph{parviglumis} abundant in the lowlands of Mexico and \emph{mexicana} abundant in the highlands. Furthermore, both \emph{parviglumis} and \emph{mexicana} occur at high densities and genetic diversity of these taxa is estimated to be high \citep{Hufford2012a, Ross-Ibarra2009}."}

### 2015-02-25 PeerJ_trackchanges.tex
Edits for PeerJ resubmission
Edits to introduction and response

Maize (\emph{Zea mays} ssp. \emph{mays}) was domesticated from the teosinte \emph{Zea mays} ssp. \emph{parviglumis} (hereafter, \emph{parviglumis}) roughly 9,000 B.P. in southwest Mexico \citep{Piperno2009, Matsuoka2002}. Maize and the teosintes are an attractive system in which to study domestication due to the abundance of genetic tools developed for maize and well-characterized domestication loci \citep{Hufford2012a, Doebley2004, Hufford2012b}. 
Additionally, large, naturally-occurring populations of both \emph{parviglumis} and the highland teosinte \emph{Zea mays} ssp. \emph{mexicana} (hereafter, \emph{mexicana}) can be found throughout Mexico \citep{Wilkes1977, Hufford2013}, and genetic diversity of these taxa is estimated to be high \citep{Ross-Ibarra2009}.

>>>>

Maize (\emph{Zea mays} ssp. \emph{mays}) was domesticated from the teosinte \emph{Zea mays} ssp. \emph{parviglumis} (hereafter, \emph{parviglumis}) roughly 9,000 B.P. in southwest Mexico \citep{Piperno2009, Matsuoka2002}. Maize and the teosintes are an attractive system in which to study domestication due to the abundance of genetic tools developed for maize and well-characterized domestication loci \citep{Hufford2012a, Doebley2004, Hufford2012b}. 
\track{Additionally, large, naturally-occurring populations of both \emph{parviglumis} and \emph{Zea mays} ssp. \emph{mexicana} (hereafter, \emph{mexicana}) can be found throughout Mexico \citep{Wilkes1977, Hufford2013}. \emph{parviglumis}, with \emph{parviglumis} abundant in the lowlands of Mexico and \emph{mexicana} abundant in the highlands. Furthermore, both \emph{parviglumis} and \emph{mexicana} occur at high densities and genetic diversity of these taxa is estimated to be high \citep{Hufford2012a, Ross-Ibarra2009}}.
